---
title: "anes"
author: "Ryan Zhang"
date: "10/12/2020"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(Hmisc)
library(rqPen)
library(vctrs)
library(foreign)
library(dplyr)
library(lubridate)
library(ggplot2)
library(survival)

set.seed(123)

```


## Create Post-Super Tuesday Dataset

```{r warning=FALSE}

naes08_phone_post <- read.spss("raw_data/naes/naes08-phone-nat-rcs-data-full.sav",
                  to.data.frame = TRUE, use.value.labels = FALSE) %>%
    filter(DATE_c > 20080129)
naes08_phone_post[naes08_phone_post == 998] <- NA
naes08_phone_post[naes08_phone_post == 999] <- NA

```


## Cleaning Data

```{r}

df08phone <- naes08_phone_post %>%

  select(RKEY, RBa02_c, 
         ABc01_c, ABo01_c,
         NAa06_c, NAa08_c,
         NBa05_c, NBa07_c,
         MA04_c, 
         ABc03_c, ABo04_c,
         ABc04_c, ABc05_c, ABc06_c, ABc07_c, 
         ABo05_c, ABo06_c, ABo07_c, ABo08_c,
         )

# Rename columns

my_candidate <- c("CLINTON", "OBAMA")
my_candidate_id <- as.integer(c(2, 7))

my_names <- c("ID", "voting", 
              "Feeling1", "Feeling2",
              "Viability1", "Viability2",
              "Electability1", "Electability2",
              "Ideology", 
              "Ideology1", "Ideology2", 
              "Lead1", "Trust1", "Experience1", "Judgement1",
              "Lead2", "Trust2", "Experience2", "Judgement2"
              )

colnames(df08phone) <- my_names

```


```{r}

df <- data.frame(my_candidate_id, my_candidate, stringsAsFactors = FALSE)
df08phone <-merge(df08phone, df, by.x = "voting", 
                  by.y = "my_candidate_id", all.x = TRUE)
names(df08phone)[names(df08phone) == "my_candidate"] <- "VoteCandidate"

```


## Normalize Variables

```{r warning=FALSE}

# 1) Normalize feeling thermometers

my_rescale1 <- function(X) { 
  if (max(X, na.rm = TRUE) == min(X, na.rm = TRUE)) 
    X / sum(X, na.rm = TRUE)
  else
    round((X - min(X, na.rm = TRUE)) /
            (max(X, na.rm = TRUE) - min(X, na.rm = TRUE)), 6)
}

df08phone[, c("NORMALIZED_FT1", "NORMALIZED_FT2")] <- t(apply(
  df08phone[, c("Feeling1", "Feeling2")],
  MARGIN = 1,
  FUN = my_rescale1))

# 2) Normalize viability and electability

my_rescale2 <- function(X) round(X / sum(X, na.rm = TRUE), 6)

df08phone[, c("NORMALIZED_VIABILITY1", "NORMALIZED_VIABILITY2")] <- t(apply(
                df08phone[, c("Viability1", "Viability2")],
                MARGIN = 1, FUN = my_rescale2))

df08phone[, c("NORMALIZED_ELECTABILITY1", "NORMALIZED_ELECTABILITY2")] <- t(apply(
                df08phone[, c("Electability1", "Electability2")],
                MARGIN = 1, FUN = my_rescale2))

# 3) Rescale ideological distance

df08phone[, c("temp_1", "temp_2")] <- square(
  df08phone[, c("Ideology1", "Ideology2")] -
    df08phone[, "Ideology"])

df08phone <- df08phone %>%
  rowwise() %>%
  mutate(temp_min = min(temp_1, temp_2)) %>%
  mutate(temp_max_min = max(temp_1, temp_2) -
           min(temp_1, temp_2)) %>%
  mutate(NORMALIZED_IDEOLOGY1 = ifelse(temp_max_min == 0,
                                       ifelse(temp_min == 0, 0, 0.5),
                                       round((temp_1 - temp_min) / 
                                               temp_max_min, 6))) %>%
  mutate(NORMALIZED_IDEOLOGY2 = ifelse(temp_max_min == 0,
                                       ifelse(temp_min == 0, 0, 0.5),
                                       round((temp_2 - temp_min) / 
                                               temp_max_min, 6))) %>%
  select(-starts_with("temp_") )

# 4) Average candidate traits

df08phone$TRAITS1 = rowMeans(
  df08phone[, c("Lead1", "Trust1", "Experience1", "Judgement1")],
  na.rm = TRUE) / 10
df08phone$TRAITS2 = rowMeans(
  df08phone[, c("Lead2", "Trust2", "Experience2", "Judgement2")],
  na.rm = TRUE) / 10

# 5) Convert NaN to NA

df08phone[df08phone == "NaN"] <- NA

```
 

## Pivoting Data (Part Two)

```{r}

# 1) Subset: df08phone_normalized_ft

my_cols <- c("ID", "VoteCandidate", "NORMALIZED_FT1", "NORMALIZED_FT2")
df <- df08phone[, my_cols]
colnames(df) <- c("ID", "VoteCandidate", my_candidate)

df <- df %>%
  pivot_longer(names_to = "Candidate", 
               values_to = "NORMALIZED_FT", 
               cols = -c(ID, VoteCandidate))
df_final_post <- df

# 2) Subset: df08phone_normalized_viability

my_cols <- c("ID", "NORMALIZED_VIABILITY1", "NORMALIZED_VIABILITY2")
df <- df08phone[, my_cols]
colnames(df) <- c("ID", my_candidate)

df <- df %>%
  pivot_longer(names_to = "Candidate", 
               values_to = "NORMALIZED_VIABILITY", 
               cols = -ID)

df_final_post = merge(df_final_post, df, by = c("ID", "Candidate"))

# Convert Vote Candidate to 0, 1

df_final_post$VoteCandidate <- 1 * (df_final_post$Candidate == df_final_post$VoteCandidate)

# 3) Subset: df08phone_normalized_electability

my_cols <- c("ID", "NORMALIZED_ELECTABILITY1", "NORMALIZED_ELECTABILITY2")
df <- df08phone[, my_cols]
colnames(df) <- c("ID", my_candidate)

df <- df %>%
  pivot_longer(names_to = "Candidate", 
               values_to = "NORMALIZED_ELECTABILITY", 
               cols = -ID)

df_final_post = merge(df_final_post, df, by = c("ID", "Candidate"))

# 4) Subset: df08phone_normalized_ideology

my_cols <- c("ID", "NORMALIZED_IDEOLOGY1", "NORMALIZED_IDEOLOGY2")
df <- df08phone[, my_cols]
colnames(df) <- c("ID", my_candidate)

df <- df %>%
  pivot_longer(names_to = "Candidate", 
               values_to = "NORMALIZED_IDEOLOGY", 
               cols = -ID)

df_final_post = merge(df_final_post, df, by = c("ID", "Candidate"))

# 5) Subset: df08phone_traits

my_cols <- c("ID", "TRAITS1", "TRAITS2")
df <- df08phone[, my_cols]
colnames(df) <- c("ID", my_candidate)

df <- df %>%
  pivot_longer(names_to = "Candidate", 
               values_to = "TRAITS", 
               cols = -ID)

df_final_post = merge(df_final_post, df, by = c("ID", "Candidate"))

```


```{r}

df_final_post[, sort(my_candidate)] <- 0

my_index <- cbind(seq_len(nrow(df_final_post)), 
                  match(df_final_post$Candidate, names(df_final_post)[-1]))

df_final_post[-1][my_index] <- 1

```


## Clean Data

```{r}

df_final_pre <- read.dta("clean_data/df08phone_d.dta") %>%
  drop_na()

df_final_post <- df_final_post %>%
  drop_na()

df_final_full <- full_join(df_final_pre, df_final_post)

naes08_phone_full <- read.spss("raw_data/naes/naes08-phone-nat-rcs-data-full.sav",
                  to.data.frame = TRUE, use.value.labels = FALSE) 

naes08_phone_full <- naes08_phone_full %>%
  mutate(DATE_c = ymd(DATE_c)) %>%
  mutate(WEEK_c = cut.Date(DATE_c, breaks = "1 week", labels = FALSE))

df_final_full_2 <- df_final_full %>%
  rowwise() %>%
  mutate(SINCERE = (NORMALIZED_FT + TRAITS) / 2,
         STRATEGIC = (NORMALIZED_VIABILITY + NORMALIZED_ELECTABILITY) / 2) %>%
  select(ID, Candidate, VoteCandidate, SINCERE, STRATEGIC) %>%
  group_by(ID) %>%
  mutate(SINCERE_MAX1 = max(SINCERE),
         STRATEGIC_MAX1 = max(STRATEGIC)) %>%
  mutate(SINCERE_MAX2 = ifelse(SINCERE == SINCERE_MAX1, 1, 0),
         STRATEGIC_MAX2 = ifelse(STRATEGIC == STRATEGIC_MAX1, 1, 0)) %>%
  filter(VoteCandidate == 1) 

```


## Graphs of Voting Types Over Time

```{r}

# Voting types over time (aggregated)

df_final_full_3 <- df_final_full_2 %>%
  full_join(naes08_phone_full, by = c("ID" = "RKEY")) %>%
  group_by(SINCERE_MAX2, STRATEGIC_MAX2, DATE_c) %>%
  count() %>%
  mutate(sincere_strategic = case_when(
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 0) ~ "irrational",
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 0) ~ "expressive",
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 1) ~ "instrumental",
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 1) ~ "ideal",
    )) %>%
  group_by(DATE_c) %>%
  drop_na() %>%
  mutate(percent = (n / sum(n)) * 100,
         df = "naes08_phone_d") 

df_final_full_3 %>%
  # filter(sincere_strategic %in% c("expressive", "instrumental")) %>%
  ggplot(aes(x = DATE_c, y = percent, color = sincere_strategic)) + 
    geom_point(size = 0.5) +
    geom_smooth(method = "loess") + 
    ylim(0, 100) + 
    scale_color_discrete(name = "Voting Type",
                         labels = c("Expressive", "Ideal", "Instrumental", "Irrational")) + 
    labs(
      title = "Voting Behavior Over Time",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Percent of Voters"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11a_voting_behavior_over_time.bmp", 
           width = 7.5, height = 4.5)

# Voting types over time (disaggregated)

df_final_full_3 <- df_final_full_2 %>%
  inner_join(naes08_phone_full, by = c("ID" = "RKEY")) %>%
  group_by(Candidate, SINCERE_MAX2, STRATEGIC_MAX2, DATE_c) %>%
  count() %>%
  mutate(sincere_strategic = case_when(
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 0) ~ 1,
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 0) ~ 2,
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 1) ~ 3,
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 1) ~ 4,
    )) %>%
  group_by(Candidate, DATE_c) %>%
  mutate(percent = (n / sum(n) * 100),
         df = "naes08_phone_d")

df_final_full_3 %>%
  filter(sincere_strategic == 4) %>%
  ggplot(aes(x = DATE_c, y = percent, color = Candidate)) + 
    geom_point(size = 0.5) + 
    geom_smooth(method = "loess") +
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Ideal Voting Over Time",
      subtitle = "2008 Democratic Nominating Contest (Disaggregated by Preferred Candidate)",
      x = "Date",
      y = "Ideal Voters (Percent)"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11b_ideal_voting_over_time.bmp", 
           width = 7.5, height = 4.5)

df_final_full_3 %>%
  filter(sincere_strategic == 2) %>%
  ggplot(aes(x = DATE_c, y = percent, color = Candidate)) + 
    geom_point(size = 0.5) + 
    geom_smooth(method = "loess") +
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Expressive Voting Over Time",
      subtitle = "2008 Democratic Nominating Contest (Disaggregated by Preferred Candidate)",
      x = "Date",
      y = "Expressive Voters (Percent)"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11b_expressive_voting_over_time.bmp", 
           width = 7.5, height = 4.5)

df_final_full_3 %>%
  filter(sincere_strategic == 3) %>%
  ggplot(aes(x = DATE_c, y = percent, color = Candidate)) + 
    geom_point(size = 0.5) + 
    geom_smooth(method = "loess") +
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Instrumental Voting Over Time",
      subtitle = "2008 Democratic Nominating Contest (Disaggregated by Preferred Candidate)",
      x = "Date",
      y = "Instrumental Voters (Percent)"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11b_instrumental_voting_over_time.bmp", 
           width = 7.5, height = 4.5)

df_final_full_3 %>%
  filter(sincere_strategic == 1) %>%
  ggplot(aes(x = DATE_c, y = percent, color = Candidate)) + 
    geom_point(size = 0.5) + 
    geom_smooth(method = "loess") +
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Irrational Voting Over Time",
      subtitle = "2008 Democratic Nominating Contest (Disaggregated by Preferred Candidate)",
      x = "Date",
      y = "Irrational Voters (Percent)"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11b_irrational_voting_over_time.bmp", 
           width = 7.5, height = 4.5)

```


## Acknowledge Bias

```{r}

# Viability -- all time, respondents primary vote choice

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999)),
         (RBa02_c %in% c(2, 4, 7))) %>%
  pivot_longer(cols = c(NAa06_c, NAa07_c, NAa08_c), names_to = "candidate", values_to = "viability") %>%
  mutate(primary_vote = case_when(
    RBa02_c == 2 ~ "Clinton",
    RBa02_c == 4 ~ "Edwards",
    RBa02_c == 7 ~ "Obama"
    )) %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c, y = viability, color = candidate)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    facet_wrap(~ primary_vote) +
    scale_color_discrete(name = "Candidate Viability",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Candidate Viability Over Time",
      subtitle = "2008 Democratic Nominating Contest (Disaggregated by Preferred Candidate)",
      x = "Month",
      y = "Viability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11d_faceted_candidate_viability.bmp", 
           width = 7.5, height = 4.5)

# Electability -- all time, respondents primary vote choice

naes08_phone_full %>%
  filter(!(NBa05_c %in% c(998, 999)),
         !(NBa06_c %in% c(998, 999)),
         !(NBa07_c %in% c(998, 999)),
         (RBa02_c %in% c(2, 4, 7))) %>%
  pivot_longer(cols = c(NBa05_c, NBa06_c, NBa07_c), names_to = "candidate", values_to = "electability") %>%
  mutate(primary_vote = case_when(
    RBa02_c == 2 ~ "Clinton",
    RBa02_c == 4 ~ "Edwards",
    RBa02_c == 7 ~ "Obama"
    )) %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c, y = electability, color = candidate)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    facet_wrap(~ primary_vote) +
    scale_color_discrete(name = "Candidate Electability",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Candidate Electability Over Time",
      subtitle = "2008 Democratic Nominating Contest (Disaggregated by Preferred Candidate)",
      x = "Month",
      y = "Electability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11d_faceted_candidate_electability.bmp", 
           width = 7.5, height = 4.5)

```


## Non-Normalized Graphs (Part 1 - Candidate Choice Over Time)

```{r message=FALSE, warning=FALSE}

######### Vote choice #########

# Candidate support graph (unstratified, entire race)

naes08_phone_full %>%
  group_by(DATE_c) %>%
  mutate(total_count = n()) %>%
  group_by(DATE_c, RBa02_c) %>%
  mutate(percent = (n() / total_count) * 100) %>%
  select(DATE_c, percent, RBa02_c) %>%
  filter(RBa02_c %in% c(2, 4, 7),
         !duplicated(RBa02_c)) %>%
  mutate(primary_vote = case_when(
    RBa02_c == 2 ~ "Clinton",
    RBa02_c == 4 ~ "Edwards",
    RBa02_c == 7 ~ "Obama"
    )) %>%
  ggplot(aes(x = DATE_c, y = percent, color = primary_vote)) + 
    geom_point(size = 0.5) + 
    geom_smooth(method = "loess") + 
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Candidate Choice Over Time",
      subtitle = "2008 Democratic Nominating Contest (Disaggregated by Preferred Candidate)",
      x = "Month",
      y = "Percent of Voters"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11f_candidate_choice_over_time.bmp", 
           width = 7.5, height = 4.5)

# Candidate support graph (unstratified, Iowa caucuses)

naes08_phone_full %>%
  group_by(DATE_c) %>%
  mutate(total_count = n()) %>%
  group_by(DATE_c, RBa02_c) %>%
  mutate(percent = (n() / total_count) * 100) %>%
  select(DATE_c, percent, RBa02_c) %>%
  filter(RBa02_c %in% c(2, 4, 7),
         !duplicated(RBa02_c)) %>%
  filter(DATE_c <= "2008-01-06",
         DATE_c >= "2007-12-29") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  mutate(primary_vote = case_when(
    RBa02_c == 2 ~ "Clinton",
    RBa02_c == 4 ~ "Edwards",
    RBa02_c == 7 ~ "Obama"
    )) %>%
  ggplot(aes(x = DATE_c, y = percent, group = iowa_caucuses)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    facet_wrap(~ primary_vote) + 
    labs(
      title = "Candidate Choice",
      subtitle = "2008 Democratic Nominating Contest (Iowa Caucuses)",
      x = "Month",
      y = "Percent of Voters"
    ) +
  ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11f_candidate_choice_iowa_caucuses.bmp", 
         width = 7.5, height = 4.5)

# Change in candidate support table (by day)

naes08_phone_full_support_day <- naes08_phone_full %>%
  group_by(DATE_c) %>%
  mutate(total_count = n()) %>%
  group_by(DATE_c, RBa02_c) %>%
  mutate(percent = (n() / total_count) * 100) %>%
  select(DATE_c, percent, RBa02_c) %>%
  filter(RBa02_c %in% c(2, 4, 7),
         !duplicated(RBa02_c)) %>%
  mutate(primary_vote = case_when(
    RBa02_c == 2 ~ "Clinton",
    RBa02_c == 4 ~ "Edwards",
    RBa02_c == 7 ~ "Obama"
    )) %>%
  drop_na() %>%
  arrange(DATE_c) %>%
  group_by(primary_vote) %>%
  mutate(daily_change = percent - lag(percent)) %>%
  select(-RBa02_c)

naes08_phone_full_support_day %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/voting_types_aggregated_day.csv")

# Change in candidate support table (by week)

naes08_phone_full_support_week <- naes08_phone_full %>%
  group_by(WEEK_c) %>%
  mutate(total_count = n()) %>%
  mutate(primary_vote = case_when(
    RBa02_c == 2 ~ "Clinton",
    RBa02_c == 4 ~ "Edwards",
    RBa02_c == 7 ~ "Obama"
    )) %>%
  group_by(WEEK_c, primary_vote) %>%
  mutate(percent = (n() / total_count) * 100) %>%
  select(WEEK_c, percent, primary_vote) %>%
  filter(primary_vote %in% c("Clinton", "Edwards", "Obama"),
         !duplicated(primary_vote)) %>%
  drop_na() %>%
  arrange(WEEK_c) %>%
  group_by(primary_vote) %>%
  mutate(weekly_change = percent - lag(percent))

naes08_phone_full_support_week %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/voting_types_aggregated_week.csv")

# Change in candidate support table (Iowa caucuses)
# Table

naes08_phone_full %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-29") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  group_by(iowa_caucuses) %>%
  mutate(total_count = n()) %>%
  group_by(iowa_caucuses, RBa02_c) %>%
  mutate(percent = (n() / total_count) * 100) %>%
  select(DATE_c, percent, RBa02_c) %>%
  filter(!duplicated(RBa02_c)) %>%
  mutate(primary_vote = case_when(
    RBa02_c == 1 ~ "Biden",
    RBa02_c == 2 ~ "Clinton",
    RBa02_c == 3 ~ "Dodd",
    RBa02_c == 4 ~ "Edwards",
    RBa02_c == 5 ~ "Gravel",
    RBa02_c == 6 ~ "Kunich",
    RBa02_c == 7 ~ "Obama",
    RBa02_c == 8 ~ "Richardson",
    RBa02_c == 9 ~ "Other",
    RBa02_c == 10 ~ "Would Not for Nominee",
    RBa02_c == 998 ~ "Don't Know",
    RBa02_c == 999 ~ "No Answer"
  )) %>%
  drop_na() %>%
  arrange(DATE_c) %>%
  group_by(primary_vote) %>%
  mutate(iowa_change = percent - lag(percent)) %>%
  select(-RBa02_c) %>%
  arrange(primary_vote, iowa_caucuses)

# Map

naes08_phone_full_map <- naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ "1 - Before Iowa",
    DATE_c > "2008-01-03" ~ "2 - After Iowa"
  )) %>%
  mutate(WFc01_c = case_when(
    WFc01_c == 1 ~ "AL",
    WFc01_c == 4 ~ "AZ",
    WFc01_c == 5 ~ "AR",
    WFc01_c == 6 ~ "CA",
    WFc01_c == 8 ~ "CO",
    WFc01_c == 9 ~ "CT",
    WFc01_c == 10 ~ "DE",
    WFc01_c == 11 ~ "DC",
    WFc01_c == 12 ~ "FL",
    WFc01_c == 13 ~ "GA",
    WFc01_c == 16 ~ "ID",
    WFc01_c == 17 ~ "IL",
    WFc01_c == 18 ~ "IN",
    WFc01_c == 19 ~ "IA",
    WFc01_c == 20 ~ "KS",
    WFc01_c == 21 ~ "KY",
    WFc01_c == 22 ~ "LA",
    WFc01_c == 23 ~ "ME",
    WFc01_c == 24 ~ "MD",
    WFc01_c == 25 ~ "MA",
    WFc01_c == 26 ~ "MI",
    WFc01_c == 27 ~ "MN",
    WFc01_c == 28 ~ "MS",
    WFc01_c == 29 ~ "MO",
    WFc01_c == 30 ~ "MT",
    WFc01_c == 31 ~ "NE",
    WFc01_c == 32 ~ "NV",
    WFc01_c == 33 ~ "NH",
    WFc01_c == 34 ~ "NJ",
    WFc01_c == 35 ~ "NM",
    WFc01_c == 36 ~ "NY",
    WFc01_c == 37 ~ "NC",
    WFc01_c == 38 ~ "ND",
    WFc01_c == 39 ~ "OH",
    WFc01_c == 40 ~ "OK",
    WFc01_c == 41 ~ "OR",
    WFc01_c == 42 ~ "PA",
    WFc01_c == 43 ~ "OK",
    WFc01_c == 44 ~ "RI",
    WFc01_c == 45 ~ "SC",
    WFc01_c == 46 ~ "SD",
    WFc01_c == 47 ~ "TN",
    WFc01_c == 48 ~ "TX",
    WFc01_c == 49 ~ "UT",
    WFc01_c == 50 ~ "VT",
    WFc01_c == 51 ~ "VA",
    WFc01_c == 53 ~ "WA",
    WFc01_c == 54 ~ "WV",
    WFc01_c == 55 ~ "WI",
    WFc01_c == 56 ~ "WY",
  )) %>%
  drop_na(NAa06_c, NAa07_c, NAa08_c) %>%
  group_by(WFc01_c, iowa_caucuses) %>%
  mutate(clinton_viability = mean(NAa06_c),
         edwards_viability = mean(NAa07_c),
         obama_viability = mean(NAa08_c)) %>%
  filter(!duplicated(clinton_viability)) %>%
  arrange(WFc01_c, iowa_caucuses) %>%
  group_by(WFc01_c) %>%
  mutate(clinton_change = clinton_viability - lag(clinton_viability),
         edwards_change = edwards_viability - lag(edwards_viability),
         obama_change = obama_viability - lag(obama_viability)) %>%
  select(WFc01_c, iowa_caucuses, 
         clinton_viability, edwards_viability, obama_viability, 
         clinton_change, edwards_change, obama_change) %>%
  arrange(WFc01_c)

# Attempt 1

coordinates <- read.csv("raw_data/state-coordinates.csv", header = TRUE, stringsAsFactors = FALSE) 

naes08_phone_full_map %>%
  left_join(coordinates, by = "WFc01_c") %>%
  ggplot() +
    geom_polygon(aes(x=lon, y=lat),color="white", fill="grey10")

# Attempt 2

coordinates2 <- get_decennial(geography = "state",
                       variables = c("P001001", "P002005"),
                       year = 2010,
                       output = "wide",
                       geometry = TRUE) %>%
  rename(state = NAME) %>%
  mutate(prop_rural = P002005/P001001,
         state = reorder(state, prop_rural))

naes08_phone_full_map %>%
  left_join(coordinates, by = "WFc01_c") %>%
  ggplot(aes(fill = clinton_change)) +
    geom_sf() + 
    # scale_size(name = "", range = c(2, 15)) +
    # guides(size = guide_legend("clinton_change")) +
    theme_void()

```


## Non-Normalized Graphs (Part 2 - Model Variables Over Time)

```{r}

######### Feeling thermometers #########

naes08_phone_full %>%
  filter(!(ABc01_c %in% c(998, 999)),
         !(ABe01_c %in% c(998, 999)),
         !(ABo01_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  pivot_longer(cols = c(ABc01_c, ABe01_c, ABo01_c), names_to = "candidate", values_to = "feeling_thermometer") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c, y = feeling_thermometer, color = candidate)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Feeling Thermometer Ratings Over Time",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Feeling Thermometer Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11g_ft_over_time.bmp", 
           width = 7.5, height = 4.5)

######### Viability #########

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  pivot_longer(cols = c(NAa06_c, NAa07_c, NAa08_c), names_to = "candidate", values_to = "viability") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c, y = viability, color = candidate)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Candidate Viability Over Time",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Viability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11g_viability_over_time.bmp", 
           width = 7.5, height = 4.5)

######### Electability #########

naes08_phone_full %>%
  filter(!(NBa05_c %in% c(998, 999)),
         !(NBa06_c %in% c(998, 999)),
         !(NBa07_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  pivot_longer(cols = c(NBa05_c, NBa06_c, NBa07_c), names_to = "candidate", values_to = "electability") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c, y = electability, color = candidate)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Candidate Electability Over Time",
      subtitle = "2008 Democratic Nominating Contest (Disaggregated by Candidate)",
      x = "Month",
      y = "Electability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11g_electability_over_time.bmp", 
           width = 7.5, height = 4.5)

######### Ideology #########

naes08_phone_full %>%
  filter(!(ABc03_c %in% c(998, 999)),
         !(ABe02_c %in% c(998, 999)),
         !(ABo04_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  pivot_longer(cols = c(ABc03_c, ABe02_c, ABo04_c), names_to = "candidate", values_to = "ideology") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c, y = ideology, color = candidate)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Candidate Ideology Over Time",
      subtitle = "2008 Democratic Nominating Contest (Disaggregated by Candidate)",
      x = "Month",
      y = "Ideological Distance"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11g_ideology_over_time.bmp", 
           width = 7.5, height = 4.5)

```


## Non-Normalized Graphs (Part 3 -- Iowa Caucus Snapshot)

```{r message=FALSE, warning=FALSE}

colors <- c("Clinton" = "#F8766D", "Edwards" = "#00BA38", "Obama" = "#619CFF")

# Favorability -- Iowa Caucus, respondents not stratified

naes08_phone_full %>%
  filter(!(ABc01_c %in% c(998, 999)),
         !(ABe01_c %in% c(998, 999)),
         !(ABo01_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) + 
    geom_smooth(aes(y = ABc01_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABe01_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABo01_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    labs(
      title = "Candidate Favorability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Feeling Thermometer Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_ft_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

# Ideology -- Iowa Caucus, respondents not stratified

naes08_phone_full %>%
  filter(!(ABc03_c %in% c(998, 999)),
         !(ABe02_c %in% c(998, 999)),
         !(ABo04_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) + 
    geom_smooth(aes(y = ABc03_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABe02_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABo04_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    labs(
      title = "Candidate Ideology (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Ideological Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_ideology_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

# Viability -- Iowa Caucus, respondents not stratified

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) + 
    geom_smooth(aes(y = NAa06_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa07_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa08_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    labs(
      title = "Candidate Viability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Viability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_viability_iowa_caucuses_unstratified.bmp", 
           width = 7.5, height = 4.5)

# Electability -- Iowa Caucus, respondents not stratified

naes08_phone_full %>%
  filter(!(NBa05_c %in% c(998, 999)),
         !(NBa06_c %in% c(998, 999)),
         !(NBa07_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) + 
    geom_smooth(aes(y = NBa05_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NBa06_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NBa07_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    labs(
      title = "Candidate Electability Over Time (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Electability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_electability_iowa_caucuses_unstratified.bmp", 
           width = 7.5, height = 4.5)

# Viability -- Iowa caucuses and New Hampshire primary, respondents stratified by education

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999)),
         !(WA03_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-13",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    (DATE_c >= "2008-01-04" & DATE_c <= "2008-01-08") ~ 1,
    (DATE_c >= "2008-01-09" & DATE_c <= "2008-01-13") ~ 2
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) + 
    geom_smooth(aes(y = NAa06_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa07_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa08_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    facet_wrap(~ WA03_c) +
    labs(
      title = "Candidate Viability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest (Stratified by Education)",
      x = "Month",
      y = "Viability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_viability_iowa_caucuses_education.bmp", 
           width = 7.5, height = 4.5)

# Electablity -- Iowa caucuses and New Hampshire primary, respondents stratified by education

naes08_phone_full %>%
  filter(!(NBa05_c %in% c(998, 999)),
         !(NBa06_c %in% c(998, 999)),
         !(NBa07_c %in% c(998, 999)),
         !(WA03_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-13",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    (DATE_c >= "2008-01-04" & DATE_c <= "2008-01-08") ~ 1,
    (DATE_c >= "2008-01-09" & DATE_c <= "2008-01-13") ~ 2
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) + 
    geom_smooth(aes(y = NBa05_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NBa06_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NBa07_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    facet_wrap(~ WA03_c) +
    labs(
      title = "Candidate Electability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest (Stratified by Education)",
      x = "Month",
      y = "Electability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_electability_iowa_caucuses_education.bmp", 
           width = 7.5, height = 4.5)

# Viability -- Iowa Caucuses, respondents stratified by party ID strength

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999)),
         MA02_c %in% c(1, 2)) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  mutate(party_strength = case_when(
    MA02_c == 1 ~ "1 - Strong",
    MA02_c == 2 ~ "2 - Weak"
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = NAa06_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa07_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa08_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) + 
    
    facet_grid(~ party_strength) +
    labs(
      title = "Candidate Viability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest (Stratified by Party ID Strength)",
      x = "Month",
      y = "Viability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_viability_iowa_caucuses_partyid_strength.bmp", 
           width = 7.5, height = 4.5)

# Electability -- Iowa Caucuses, respondents stratified by party ID strength

naes08_phone_full %>%
  filter(!(NBa05_c %in% c(998, 999)),
         !(NBa06_c %in% c(998, 999)),
         !(NBa07_c %in% c(998, 999)),
         MA02_c %in% c(1, 2)) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  mutate(party_strength = case_when(
    MA02_c == 1 ~ "1 - Strong",
    MA02_c == 2 ~ "2 - Weak"
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = NBa05_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NBa06_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NBa07_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) + 
    
    facet_grid(~ party_strength) +
    labs(
      title = "Candidate Electability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest (Stratified by Party ID Strength)",
      x = "Month",
      y = "Electability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_electability_iowa_caucuses_partyid_strength.bmp", 
           width = 7.5, height = 4.5)

# Viability -- Iowa Caucuses, respondents stratified by political interest

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999)),
         KA01_c %in% c(1, 2, 3, 4)) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  mutate(political_interest = case_when(
    KA01_c == 1 ~ "1 - Closely",
    KA01_c == 2 ~ "1 - Closely",
    KA01_c == 3 ~ "2 - Not Closely",
    KA01_c == 4 ~ "2 - Not Closely"
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = NAa06_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa07_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa08_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    facet_wrap(~ political_interest) +
    labs(
      title = "Candidate Viability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest (Stratified by Interest in Politics)",
      x = "Month",
      y = "Viability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_viability_iowa_caucuses_political_interest.bmp", 
           width = 7.5, height = 4.5)

# Electability -- Iowa Caucuses, respondents stratified by political interest

naes08_phone_full %>%
  filter(!(NBa05_c %in% c(998, 999)),
         !(NBa06_c %in% c(998, 999)),
         !(NBa07_c %in% c(998, 999)),
         KA01_c %in% c(1, 2, 3, 4)) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  mutate(political_interest = case_when(
    KA01_c == 1 ~ "1 - Closely",
    KA01_c == 2 ~ "1 - Closely",
    KA01_c == 3 ~ "2 - Not Closely",
    KA01_c == 4 ~ "2 - Not Closely"
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = NBa05_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NBa06_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NBa07_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    facet_wrap(~ political_interest) +
    labs(
      title = "Candidate Electability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest (Stratified by Interest in Politics)",
      x = "Month",
      y = "Electability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_electability_iowa_caucuses_political_interest.bmp", 
           width = 7.5, height = 4.5)

# Viability -- Iowa Caucuses, respondents stratified by whether they knew who won Iowa
# Graph

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999)),
         NAc02_c %in% c(5, 7, 8)) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  mutate(political_interest = case_when(
    NAc02_c == 5 ~ "1 - Obama",
    NAc02_c == 7 ~ "2 - Don't Know",
    NAc02_c == 8 ~ "2 - Don't Know"
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = NAa06_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa07_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa08_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    facet_wrap(~ political_interest) +
    labs(
      title = "Candidate Viability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest (Stratified by Knowledge of Iowa Caucuses)",
      x = "Month",
      y = "Viability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_viability_iowa_caucuses_iowa_results.bmp", 
           width = 7.5, height = 4.5)

# Table

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999)),
         NAc02_c %in% c(5, 7, 8)) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-29") %>%
  mutate(NAc02_c = case_when(
    NAc02_c == 5 ~ "1 - Obama",
    NAc02_c == 7 ~ "2 - Don't Know",
    NAc02_c == 8 ~ "2 - Don't Know"
  )) %>%
  drop_na(NAa06_c, NAa07_c, NAa08_c) %>%
  group_by(NAc02_c) %>%
  mutate(clinton_viability = mean(NAa06_c),
         edwards_viability = mean(NAa07_c),
         obama_viability = mean(NAa08_c)) %>%
  filter(!duplicated(clinton_viability)) %>%
  select(NAc02_c, clinton_viability, edwards_viability, obama_viability) %>%
  arrange(NAc02_c)

# Electability -- Iowa Caucuses, respondents stratified by whether they knew who won Iowa
# Graph

naes08_phone_full %>%
  filter(!(NBa05_c %in% c(998, 999)),
         !(NBa06_c %in% c(998, 999)),
         !(NBa07_c %in% c(998, 999)),
         NAc02_c %in% c(5, 7, 8)) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  mutate(political_interest = case_when(
    NAc02_c == 5 ~ "1 - Obama",
    NAc02_c == 7 ~ "2 - Don't Know",
    NAc02_c == 8 ~ "2 - Don't Know"
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = NBa05_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NBa06_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NBa07_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    facet_wrap(~ political_interest) +
    labs(
      title = "Candidate Electability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest (Stratified by Knowledge of Iowa Caucuses)",
      x = "Month",
      y = "Electability Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11h_electability_iowa_caucuses_iowa_results.bmp", 
           width = 7.5, height = 4.5)

# Table

naes08_phone_full %>%
  filter(!(NBa05_c %in% c(998, 999)),
         !(NBa06_c %in% c(998, 999)),
         !(NBa07_c %in% c(998, 999)),
         NAc02_c %in% c(5, 7, 8)) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-29") %>%
  mutate(NAc02_c = case_when(
    NAc02_c == 5 ~ "1 - Obama",
    NAc02_c == 7 ~ "2 - Don't Know",
    NAc02_c == 8 ~ "2 - Don't Know"
  )) %>%
  drop_na(NBa05_c, NBa06_c, NBa07_c) %>%
  group_by(NAc02_c) %>%
  mutate(clinton_electability = mean(NBa05_c),
         edwards_electability = mean(NBa06_c),
         obama_electability = mean(NBa07_c)) %>%
  filter(!duplicated(clinton_electability)) %>%
  select(NAc02_c, clinton_electability, edwards_electability, obama_electability) %>%
  arrange(NAc02_c)

```


## Non-Normalized Graphs (Part 4)

```{r message=FALSE, warning=FALSE}

# Experience (over time)

naes08_phone_full %>%
  filter(!(ABc06_c %in% c(998, 999)),
         !(ABe05_c %in% c(998, 999)),
         !(ABo07_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  pivot_longer(cols = c(ABc06_c, ABe05_c, ABo07_c), names_to = "candidate", values_to = "experience") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c, y = experience, color = candidate)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Candidate Experience"
    ) 

# Experience (Iowa caucuses)

naes08_phone_full %>%
  filter(!(ABc06_c %in% c(998, 999)),
         !(ABe05_c %in% c(998, 999)),
         !(ABo07_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = ABc06_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABe05_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABo07_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    labs(
      title = "Candidate Experience (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Experience Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11i_experience_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

# Judgement (over time)

naes08_phone_full %>%
  filter(!(ABc07_c %in% c(998, 999)),
         !(ABe06_c %in% c(998, 999)),
         !(ABo08_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  pivot_longer(cols = c(ABc07_c, ABe06_c, ABo08_c), names_to = "candidate", values_to = "judgement") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c, y = judgement, color = candidate)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Candidate Judgement Over Time"
    ) 

# Judgement (Iowa caucuses)

naes08_phone_full %>%
  filter(!(ABc07_c %in% c(998, 999)),
         !(ABe06_c %in% c(998, 999)),
         !(ABo08_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = ABc07_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABe06_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABo08_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    labs(
      title = "Candidate Judgement (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Judgement Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11i_judgement_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

# Strong leader (over time)

naes08_phone_full %>%
  filter(!(ABc04_c %in% c(998, 999)),
         !(ABe03_c %in% c(998, 999)),
         !(ABo05_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  pivot_longer(cols = c(ABc04_c, ABe03_c, ABo05_c), names_to = "candidate", values_to = "leadership") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c, y = leadership, color = candidate)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Candidate Leadership Over Time"
    ) 

# Strong leader (Iowa caucuses)

naes08_phone_full %>%
  filter(!(ABc04_c %in% c(998, 999)),
         !(ABe03_c %in% c(998, 999)),
         !(ABo05_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = ABc04_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABe03_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABo05_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    labs(
      title = "Candidate Leadership (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Strong Leader Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11i_leadership_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

# Trustworthiness (over time)

naes08_phone_full %>%
  filter(!(ABc05_c %in% c(998, 999)),
         !(ABe04_c %in% c(998, 999)),
         !(ABo06_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  pivot_longer(cols = c(ABc05_c, ABe04_c, ABo06_c), names_to = "candidate", values_to = "trustworthiness") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c, y = trustworthiness, color = candidate)) + 
    geom_smooth(method = "loess", se = FALSE) + 
    scale_color_discrete(name = "Candidate",
                         labels = c("Clinton", "Edwards", "Obama")) + 
    labs(
      title = "Candidate Trustworthiness Over Time"
    ) 

# Trustworthiness (Iowa caucuses)

naes08_phone_full %>%
  filter(!(ABc05_c %in% c(998, 999)),
         !(ABe04_c %in% c(998, 999)),
         !(ABo06_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = ABc05_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABe04_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ABo06_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    labs(
      title = "Candidate Trustworthiness (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Trustworthiness Rating"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11i_trustworthiness_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

#####################

# Whether Iraq war was worth it -- before and after Iowa Caucuses 

naes08_phone_full %>%
  filter(!(CDb01_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ "1 - Before Iowa",
    DATE_c > "2008-01-03" ~ "2 - After Iowa",
  )) %>%
  group_by(iowa_caucuses) %>%
  mutate(total_count = n()) %>%
  group_by(CDb01_c, iowa_caucuses) %>%
  mutate(percent = (n() / total_count) * 100) %>%
  filter(!duplicated(CDb01_c)) %>%
  ggplot(aes(x = CDb01_c, fill = CDb01_c)) +
    geom_col(aes(y = percent)) +
    facet_wrap(~ iowa_caucuses) +
    theme(legend.position = "none") +
    labs(
      title = "Attitudes Towards the Iraq War",
      subtitle = "2008 Democratic Nominating Contest (Iowa Caucuses)",
      x = "Response",
      y = "Percent of Respondents",
      caption = "Exact dates range from December 30, 2007 to January 8, 2008. Answer \n choices include 1) Withdraw as Soon as Possible, 2) Set Withdrawal Deadline, \n 3) Keep Troops Until Stable Government, and 4) None of These."
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11j_foreign_policy_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

# Views on health care -- before and after Iowa Caucuses 

naes08_phone_full %>%
  filter(!(CCa01_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ "1 - Before Iowa",
    DATE_c > "2008-01-03" ~ "2 - After Iowa",
  )) %>%
  group_by(iowa_caucuses) %>%
  mutate(total_count = n()) %>%
  group_by(CCa01_c, iowa_caucuses) %>%
  mutate(percent = (n() / total_count) * 100) %>%
  filter(!duplicated(CCa01_c)) %>%
  ggplot(aes(x = CCa01_c, fill = CCa01_c)) +
    geom_col(aes(y = percent)) +
    facet_wrap(~ iowa_caucuses) +
    theme(legend.position = "none") +
    labs(
      title = "Views on Health Care",
      subtitle = "2008 Democratic Nominating Contest (Iowa Caucuses)",
      x = "Response",
      y = "Percent of Respondents",
      caption = "Exact dates range from December 30, 2007 to January 8, 2008. Answer \n choices include 1) One Government Program, 2) Current System, and 3) Neither."
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11j_healthcare_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

# Views on the economy -- before and after Iowa Caucuses 

naes08_phone_full %>%
  filter(!(CBb01_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ "1 - Before Iowa",
    DATE_c > "2008-01-03" ~ "2 - After Iowa",
  )) %>%
  group_by(iowa_caucuses) %>%
  mutate(total_count = n()) %>%
  group_by(CBb01_c, iowa_caucuses) %>%
  mutate(percent = (n() / total_count) * 100) %>%
  filter(!duplicated(CBb01_c)) %>%
  ggplot(aes(x = CBb01_c, fill = CBb01_c)) +
    geom_col(aes(y = percent)) +
    facet_wrap(~ iowa_caucuses) +
    theme(legend.position = "none") +
    labs(
      title = "Views on Economic Policy",
      subtitle = "2008 Democratic Nominating Contest (Iowa Caucuses)",
      x = "Response",
      y = "Percent of Respondents",
      caption = "Exact dates range from December 30, 2007 to January 8, 2008. Answer \n choices include 1) Cut Taxes, 2) Keep Taxes as They Are, 3) Raise Taxes if Necessary, and 4) None of These."
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11j_economy_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

# Political orientation -- before and after Iowa Caucuses 

naes08_phone_full %>%
  filter(!(MA04_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ "1 - Before Iowa",
    DATE_c > "2008-01-03" ~ "2 - After Iowa",
  )) %>%
  group_by(iowa_caucuses) %>%
  mutate(total_count = n()) %>%
  group_by(MA04_c, iowa_caucuses) %>%
  mutate(percent = (n() / total_count) * 100) %>%
  filter(!duplicated(MA04_c)) %>%
  ggplot(aes(x = MA04_c, fill = MA04_c)) +
    geom_col(aes(y = percent)) +
    facet_wrap(~ iowa_caucuses) +
    theme(legend.position = "none") +
    labs(
      title = "Ideological Placement",
      subtitle = "2008 Democratic Nominating Contest (Iowa Caucuses)",
      x = "Response",
      y = "Percent of Respondents",
      caption = "Exact dates range from December 30, 2007 to January 8, 2008. Answer \n choices include 1) Very Conservative, 2) Somewhat Conservative, 3) Moderate, 4) Somewhat Liberal, and 5) Very Liberal." 
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11j_political_orientation_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

#####################

# Political interest (over time)

naes08_phone_full %>%
  filter(!(KA01_c %in% c(998, 999)),
         !(KB01_c %in% c(998, 999)),
         !(KD01_c %in% c(998, 999)),
         !(KE01_c %in% c(998, 999)),
         !(KG01_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c)) + 
    geom_smooth(aes(y = KA01_c), method = "loess", se = FALSE, color = "#F8766D") +
    geom_smooth(aes(y = KB01_c), method = "loess", se = FALSE, color = "#00BA38") +
    # geom_smooth(aes(y = KD01_c), method = "loess", se = FALSE) +
    # geom_smooth(aes(y = KE01_c), method = "loess", se = FALSE) +
    # geom_smooth(aes(y = KG01_c), method = "loess", se = FALSE) +
    labs(
      title = "Days Discussed Politics in Past Week"
    ) 

# Political interest (Iowa caucuses)

naes08_phone_full %>%
  filter(!(KA01_c %in% c(998, 999)),
         !(KB01_c %in% c(998, 999)),
         !(KD01_c %in% c(998, 999)),
         !(KE01_c %in% c(998, 999)),
         !(KG01_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    # geom_smooth(aes(y = KA01_c), method = "loess", se = FALSE, color = "#F8766D") +
    geom_smooth(aes(y = KB01_c), method = "loess", se = FALSE) +
    # geom_smooth(aes(y = KD01_c), method = "loess", se = FALSE) +
    # geom_smooth(aes(y = KE01_c), method = "loess", se = FALSE) +
    # geom_smooth(aes(y = KG01_c), method = "loess", se = FALSE) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    labs(
      title = "Days Discussed Politics in Past Week (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Month",
      y = "Number of Days"
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11j_days_discussing_politics_iowa_caucuses.bmp", 
           width = 7.5, height = 4.5)

```

## Mentions and Regressions

```{r}

# Calculating mentions (Iowa caucuses)

health_terms <- c("health", "insur", "drug")
economy_terms <- c("job", "econ", "stock", "market", "hous", "employ")
war_terms <- c("war", "terror", "iraq", "secur")

naes08_phone_full %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  mutate(CA01r1v_c = tolower(CA01r1v_c)) %>%
  mutate(health = ifelse(grepl(paste(health_terms, collapse = "|"), 
                               CA01r1v_c), 1, 0),
         economy = ifelse(grepl(paste(economy_terms, collapse = "|"),
                                CA01r1v_c), 1, 0),
         war = ifelse(grepl(paste(war_terms, collapse = "|"),
                                CA01r1v_c), 1, 0)) %>%
  select(CA01r1v_c, health, economy, war, DATE_c, iowa_caucuses) %>%
  arrange(DATE_c) %>%
  group_by(iowa_caucuses) %>%
  mutate(percentage_health = sum(health) / n(),
         percentage_economy = sum(economy) / n(),
         percentage_war = sum(war) / n()) %>%
  filter(!duplicated(percentage_health)) %>%
  select(c(iowa_caucuses, percentage_health, percentage_economy, percentage_war))

# Calculating regressions (over time)

df_final_full_reg <- df_final_full %>%
  full_join(naes08_phone_full, by = c("ID" = "RKEY")) %>%
  select(WEEK_c, DATE_c, ID, VoteCandidate, CLINTON, EDWARDS, NORMALIZED_FT, NORMALIZED_VIABILITY,
         NORMALIZED_ELECTABILITY, NORMALIZED_IDEOLOGY)

reg_to_df <- function(x) {
  data.frame(variable = rownames(summary(x)$coef),
  coef = summary(x)$coef[, 1],
  se = summary(x)$coef[, 3],
  exp_coef = summary(x)$coef[, 2])
}

factor_odds <- function(x) {
  exp(x)
}

for(i in 1:6) {
  assign(paste0("df_final_full_reg_wk", i), df_final_full_reg %>%
    filter(WEEK_c == i) %>%
    clogit(data = ., formula = VoteCandidate ~ CLINTON + 
           EDWARDS + NORMALIZED_FT + NORMALIZED_VIABILITY + 
           NORMALIZED_ELECTABILITY + NORMALIZED_IDEOLOGY + 
           strata(ID)) %>%
    reg_to_df(.) %>%
    mutate(week = i)) 
}

for(i in 7:25) {
  assign(paste0("df_final_full_reg_wk", i), df_final_full_reg %>%
    filter(WEEK_c == i) %>%
    clogit(formula = VoteCandidate ~ CLINTON + 
             NORMALIZED_FT + NORMALIZED_VIABILITY + 
             NORMALIZED_ELECTABILITY + NORMALIZED_IDEOLOGY + 
             strata(ID)) %>%
    reg_to_df(.) %>%
    mutate(week = i))
}

for(i in 1:25) {

  df_final_full_reg_all <- rbind(paste0("df_final_full_reg_wk", i))
  
}

df_final_full_reg_all <- data.frame(rbind(df_final_full_reg_wk1, 
                                  df_final_full_reg_wk2, 
                                  df_final_full_reg_wk3, 
                                  df_final_full_reg_wk4, 
                                  df_final_full_reg_wk5, 
                                  df_final_full_reg_wk6, 
                                  df_final_full_reg_wk7, 
                                  df_final_full_reg_wk8, 
                                  df_final_full_reg_wk9, 
                                  df_final_full_reg_wk10, 
                                  df_final_full_reg_wk11, 
                                  df_final_full_reg_wk12, 
                                  df_final_full_reg_wk13, 
                                  df_final_full_reg_wk14, 
                                  df_final_full_reg_wk15, 
                                  df_final_full_reg_wk16, 
                                  df_final_full_reg_wk17, 
                                  df_final_full_reg_wk18, 
                                  df_final_full_reg_wk19, 
                                  df_final_full_reg_wk20, 
                                  df_final_full_reg_wk21, 
                                  df_final_full_reg_wk22, 
                                  df_final_full_reg_wk23, 
                                  df_final_full_reg_wk24, 
                                  df_final_full_reg_wk25)) %>%
  rowwise() %>%
  mutate(fctodds = factor_odds(coef))

interval1 <- -qnorm((1 - 0.9) / 2)  # 90% CI multiplier
interval2 <- -qnorm((1 - 0.95) / 2)  # 95% CI multiplier

# Graph of coefficients
# All

df_final_full_reg_all %>%
  filter(week %in% 1:25) %>%
  filter(variable %in% c("NORMALIZED_VIABILITY", "NORMALIZED_ELECTABILITY", 
                         "NORMALIZED_FT", "NORMALIZED_IDEOLOGY")) %>%
  mutate(variable = factor(variable, levels = c("NORMALIZED_VIABILITY", 
                                                "NORMALIZED_ELECTABILITY", 
                                                "NORMALIZED_FT", 
                                                "NORMALIZED_IDEOLOGY"),
                           labels = c("Viability", "Electability",
                                      "Feeling Thermometer", "Ideology"))) %>%
  ggplot(aes(x = week, y = coef)) +
    geom_hline(yintercept = 0, colour = gray(1 / 2), lty = 2) +
    geom_pointrange(aes(ymin = coef - se * interval2,
                        ymax = coef + se * interval2),
                    lwd = 1 / 2, shape = 21, fill = "WHITE") +
    geom_smooth(method = "loess") +
    theme_bw() +
    facet_wrap(~ variable, nrow = 2) + 
    theme(legend.position = "none") + 
    labs(
      title = "Coefficients Over Time",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Week",
      y = "Coefficient",
      caption = "Point estimates and 95% confidence intervals are shown."
    )

# Viability

df_final_full_reg_all %>%
  filter(week %in% 1:25) %>%
  filter(variable %in% c("NORMALIZED_VIABILITY")) %>%
  mutate(variable = factor(variable, levels = c("NORMALIZED_VIABILITY"),
                           labels = c("Viability"))) %>%
  ggplot(aes(x = week, y = coef)) +
    geom_hline(yintercept = 0, colour = gray(1 / 2), lty = 2) +
    geom_pointrange(aes(ymin = coef - se * interval2,
                        ymax = coef + se * interval2),
                    lwd = 1 / 2, shape = 21, fill = "WHITE") +
    geom_smooth(method = "loess") +
    theme_bw() +
    theme(legend.position = "none") + 
    labs(
      title = "Viability Coefficient Over Time",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Week",
      y = "Coefficient",
      caption = "Point estimates and 95% confidence intervals are shown."
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11k_viability_coefficients_over_time.bmp", 
           width = 7.5, height = 4.5)

# Electability

df_final_full_reg_all %>%
  filter(week %in% 1:25) %>%
  filter(variable %in% c("NORMALIZED_ELECTABILITY")) %>%
  mutate(variable = factor(variable, levels = c("NORMALIZED_ELECTABILITY"),
                           labels = c("Electability"))) %>%
  ggplot(aes(x = week, y = coef)) +
    geom_hline(yintercept = 0, colour = gray(1 / 2), lty = 2) +
    geom_pointrange(aes(ymin = coef - se * interval2,
                        ymax = coef + se * interval2),
                    lwd = 1 / 2, shape = 21, fill = "WHITE") +
    geom_smooth(method = "loess") +
    theme_bw() +
    theme(legend.position = "none") + 
    labs(
      title = "Electability Coefficient Over Time",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Week",
      y = "Coefficient",
      caption = "Point estimates and 95% confidence intervals are shown."
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11k_electability_coefficients_over_time.bmp", 
           width = 7.5, height = 4.5)

# Feeling thermometer

df_final_full_reg_all %>%
  filter(week %in% 1:25) %>%
  filter(variable %in% c("NORMALIZED_FT")) %>%
  mutate(variable = factor(variable, levels = c("NORMALIZED_FT"),
                           labels = c("Feeling Thermometer"))) %>%
  ggplot(aes(x = week, y = coef)) +
    geom_hline(yintercept = 0, colour = gray(1 / 2), lty = 2) +
    geom_pointrange(aes(ymin = coef - se * interval2,
                        ymax = coef + se * interval2),
                    lwd = 1 / 2, shape = 21, fill = "WHITE") +
    geom_smooth(method = "loess") +
    ylim(1, 8) + 
    theme_bw() +
    theme(legend.position = "none") + 
    labs(
      title = "Favorability Coefficient Over Time",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Week",
      y = "Coefficient",
      caption = "Point estimates and 95% confidence intervals are shown."
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11k_ft_coefficients_over_time.bmp", 
           width = 7.5, height = 4.5)

# Ideology

df_final_full_reg_all %>%
  filter(week %in% 1:25) %>%
  filter(variable %in% c("NORMALIZED_IDEOLOGY")) %>%
  mutate(variable = factor(variable, levels = c("NORMALIZED_IDEOLOGY"),
                           labels = c("Ideology"))) %>%
  ggplot(aes(x = week, y = coef)) +
    geom_hline(yintercept = 0, colour = gray(1 / 2), lty = 2) +
    geom_pointrange(aes(ymin = coef - se * interval2,
                        ymax = coef + se * interval2),
                    lwd = 1 / 2, shape = 21, fill = "WHITE") +
    geom_smooth(method = "loess") +
    theme_bw() +
    theme(legend.position = "none") + 
    labs(
      title = "Ideological Distance Coefficient Over Time",
      subtitle = "2008 Democratic Nominating Contest",
      x = "Week",
      y = "Coefficient",
      caption = "Point estimates and 95% confidence intervals are shown."
    ) +
    ggsave("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure11/11k_ideological_distance_coefficients_over_time.bmp", 
           width = 7.5, height = 4.5)

```

## Calculating Weekly Changes

```{r message=FALSE, warning=FALSE}

# Change per week (voting types aggregated together)

df_final_full_3 <- df_final_full_2 %>%
  full_join(naes08_phone_full, by = c("ID" = "RKEY")) %>%
  group_by(SINCERE_MAX2, STRATEGIC_MAX2, WEEK_c) %>%
  count() %>%
  mutate(sincere_strategic = case_when(
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 0) ~ "irrational",
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 0) ~ "expressive",
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 1) ~ "instrumental",
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 1) ~ "ideal",
    )) %>%
  group_by(WEEK_c) %>%
  drop_na() %>%
  mutate(percent = n / sum(n)) %>%
  group_by(SINCERE_MAX2, STRATEGIC_MAX2) %>%
  mutate(percent_change = percent - lag(percent))

df_final_full_3 %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/voting_types_aggregated_week.csv")

# Change per week (voting types disaggregated by candidate)

df_final_full_3 <- df_final_full_2 %>%
  inner_join(naes08_phone_full, by = c("ID" = "RKEY")) %>%
  group_by(Candidate, SINCERE_MAX2, STRATEGIC_MAX2, WEEK_c) %>%
  count() %>%
  mutate(sincere_strategic = case_when(
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 0) ~ 1,
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 0) ~ 2,
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 1) ~ 3,
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 1) ~ 4,
    )) %>%
  group_by(Candidate, WEEK_c) %>%
  mutate(percent = n / sum(n)) %>%
  group_by(SINCERE_MAX2, STRATEGIC_MAX2, Candidate) %>%
  mutate(percent_change = percent - lag(percent))

df_final_full_3 %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/voting_types_candidate_week.csv")

# Change per week (candidate feeling thermometer)

naes08_phone_full_ft_week <- naes08_phone_full %>%
  filter(!(ABc01_c %in% c(998, 999)),
         !(ABe01_c %in% c(998, 999)),
         !(ABo01_c %in% c(998, 999))) %>%
  pivot_longer(cols = c(ABc01_c, ABe01_c, ABo01_c), names_to = "candidate", values_to = "feeling_thermometer") %>%
  mutate(candidate = case_when(
    candidate == "ABc01_c" ~ "Clinton",
    candidate == "ABe01_c" ~ "Edwards",
    candidate == "ABo01_c" ~ "Obama"
    )) %>%
  select(WEEK_c, candidate, feeling_thermometer) %>%
  drop_na() %>%
  group_by(WEEK_c, candidate) %>%
  mutate(weekly_average = mean(feeling_thermometer)) %>%
  filter(!duplicated(WEEK_c, candidate)) %>%
  arrange(WEEK_c) %>%
  select(-feeling_thermometer) %>%
  group_by(candidate) %>%
  mutate(change = weekly_average - lag(weekly_average))

naes08_phone_full_ft_week %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/feeling_thermometer_week.csv")

# Change per day (candidate feeling thermometer)

naes08_phone_full_ft_day <- naes08_phone_full %>%
  filter(!(ABc01_c %in% c(998, 999)),
         !(ABe01_c %in% c(998, 999)),
         !(ABo01_c %in% c(998, 999))) %>%
  pivot_longer(cols = c(ABc01_c, ABe01_c, ABo01_c), names_to = "candidate", values_to = "feeling_thermometer") %>%
  mutate(candidate = case_when(
    candidate == "ABc01_c" ~ "Clinton",
    candidate == "ABe01_c" ~ "Edwards",
    candidate == "ABo01_c" ~ "Obama"
    )) %>%
  select(DATE_c, candidate, feeling_thermometer) %>%
  drop_na() %>%
  group_by(DATE_c, candidate) %>%
  mutate(weekly_average = mean(feeling_thermometer)) %>%
  filter(!duplicated(DATE_c, candidate)) %>%
  arrange(DATE_c) %>%
  select(-feeling_thermometer) %>%
  group_by(candidate) %>%
  mutate(change = weekly_average - lag(weekly_average))

naes08_phone_full_ft_day %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/feeling_thermometer_day.csv")

# Change per week (candidate viability)

naes08_phone_full_viability_week <- naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999))) %>%
  pivot_longer(cols = c(NAa06_c, NAa07_c, NAa08_c), names_to = "candidate", values_to = "viability") %>%
  mutate(candidate = case_when(
    candidate == "NAa06_c" ~ "Clinton",
    candidate == "NAa07_c" ~ "Edwards",
    candidate == "NAa08_c" ~ "Obama"
    )) %>%
  select(WEEK_c, candidate, viability) %>%
  drop_na() %>%
  group_by(WEEK_c, candidate) %>%
  mutate(weekly_average = mean(viability)) %>%
  filter(!duplicated(WEEK_c, candidate)) %>%
  arrange(WEEK_c) %>%
  select(-viability) %>%
  group_by(candidate) %>%
  mutate(change = weekly_average - lag(weekly_average))

naes08_phone_full_viability_week %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/viability_week.csv")

# Change per day (candidate viability)

naes08_phone_full_viability_day <- naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999))) %>%
  pivot_longer(cols = c(NAa06_c, NAa07_c, NAa08_c), names_to = "candidate", values_to = "viability") %>%
  mutate(candidate = case_when(
    candidate == "NAa06_c" ~ "Clinton",
    candidate == "NAa07_c" ~ "Edwards",
    candidate == "NAa08_c" ~ "Obama"
    )) %>%
  select(DATE_c, candidate, viability) %>%
  drop_na() %>%
  group_by(DATE_c, candidate) %>%
  mutate(weekly_average = mean(viability)) %>%
  filter(!duplicated(DATE_c, candidate)) %>%
  arrange(DATE_c) %>%
  select(-viability) %>%
  group_by(candidate) %>%
  mutate(change = weekly_average - lag(weekly_average))

naes08_phone_full_viability_day %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/viability_day.csv")

# Change per week (candidate electability)

naes08_phone_full_electability_week <- naes08_phone_full %>%
  filter(!(NBa05_c %in% c(998, 999)),
         !(NBa06_c %in% c(998, 999)),
         !(NBa07_c %in% c(998, 999))) %>%
  pivot_longer(cols = c(NBa05_c, NBa06_c, NBa07_c), names_to = "candidate", values_to = "electability") %>%
  mutate(candidate = case_when(
    candidate == "NBa05_c" ~ "Clinton",
    candidate == "NBa06_c" ~ "Edwards",
    candidate == "NBa07_c" ~ "Obama"
    )) %>%
  select(WEEK_c, candidate, electability) %>%
  drop_na() %>%
  group_by(WEEK_c, candidate) %>%
  mutate(weekly_average = mean(electability)) %>%
  filter(!duplicated(WEEK_c, candidate)) %>%
  arrange(WEEK_c) %>%
  select(-electability) %>%
  group_by(candidate) %>%
  mutate(change = weekly_average - lag(weekly_average))

naes08_phone_full_electability_week %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/electability_week.csv")

# Change per day (candidate electability)

naes08_phone_full_electability_day <- naes08_phone_full %>%
  filter(!(NBa05_c %in% c(998, 999)),
         !(NBa06_c %in% c(998, 999)),
         !(NBa07_c %in% c(998, 999))) %>%
  pivot_longer(cols = c(NBa05_c, NBa06_c, NBa07_c), names_to = "candidate", values_to = "electability") %>%
  mutate(candidate = case_when(
    candidate == "NBa05_c" ~ "Clinton",
    candidate == "NBa06_c" ~ "Edwards",
    candidate == "NBa07_c" ~ "Obama"
    )) %>%
  select(DATE_c, candidate, electability) %>%
  drop_na() %>%
  group_by(DATE_c, candidate) %>%
  mutate(weekly_average = mean(electability)) %>%
  filter(!duplicated(DATE_c, candidate)) %>%
  arrange(DATE_c) %>%
  select(-electability) %>%
  group_by(candidate) %>%
  mutate(change = weekly_average - lag(weekly_average))

naes08_phone_full_electability_day %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/electability_day.csv")

# Change per week (candidate ideology)

naes08_phone_full_ideology_week <- naes08_phone_full %>%
  filter(!(ABc03_c %in% c(998, 999)),
         !(ABe02_c %in% c(998, 999)),
         !(ABo04_c %in% c(998, 999))) %>%
  pivot_longer(cols = c(ABc03_c, ABe02_c, ABo04_c), names_to = "candidate", values_to = "ideology") %>%
  mutate(candidate = case_when(
    candidate == "ABc03_c" ~ "Clinton",
    candidate == "ABe02_c" ~ "Edwards",
    candidate == "ABo04_c" ~ "Obama"
    )) %>%
  select(WEEK_c, candidate, ideology) %>%
  drop_na() %>%
  group_by(WEEK_c, candidate) %>%
  mutate(weekly_average = mean(ideology)) %>%
  filter(!duplicated(WEEK_c, candidate)) %>%
  arrange(WEEK_c) %>%
  select(-ideology) %>%
  group_by(candidate) %>%
  mutate(change = weekly_average - lag(weekly_average))

naes08_phone_full_ideology_week %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/ideology_week.csv")

# Change per day (candidate ideology)

naes08_phone_full_ideology_day <- naes08_phone_full %>%
  filter(!(ABc03_c %in% c(998, 999)),
         !(ABe02_c %in% c(998, 999)),
         !(ABo04_c %in% c(998, 999))) %>%
  pivot_longer(cols = c(ABc03_c, ABe02_c, ABo04_c), names_to = "candidate", values_to = "ideology") %>%
  mutate(candidate = case_when(
    candidate == "ABc03_c" ~ "Clinton",
    candidate == "ABe02_c" ~ "Edwards",
    candidate == "ABo04_c" ~ "Obama"
    )) %>%
  select(DATE_c, candidate, ideology) %>%
  drop_na() %>%
  group_by(DATE_c, candidate) %>%
  mutate(weekly_average = mean(ideology)) %>%
  filter(!duplicated(DATE_c, candidate)) %>%
  arrange(DATE_c) %>%
  select(-ideology) %>%
  group_by(candidate) %>%
  mutate(change = weekly_average - lag(weekly_average))

naes08_phone_full_ideology_day %>%
  write.csv("/Users/ryan/Google Drive/2020_2021/Thesis/Figures/Figure13/ideology_day.csv")

```


```{r include=FALSE}

rm(list = ls())

```


## Miscellaneous

```{r}



```



```{r}

# Graphs of Normalized Variables

# By week (voting types aggregated together)

df_final_full_3 <- df_final_full_2 %>%
  full_join(naes08_phone_full, by = c("ID" = "RKEY")) %>%
  group_by(SINCERE_MAX2, STRATEGIC_MAX2, WEEK_c) %>%
  count() %>%
  mutate(sincere_strategic = case_when(
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 0) ~ "irrational",
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 0) ~ "expressive",
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 1) ~ "instrumental",
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 1) ~ "ideal",
    )) %>%
  group_by(WEEK_c) %>%
  drop_na() %>%
  mutate(percent = n / sum(n),
         df = "naes08_phone_d")

df_final_full_3 %>%
  ggplot(aes(x = WEEK_c, y = percent, color = sincere_strategic)) + 
    geom_point(size = 0.5) +
    geom_smooth(method = "loess")

# By week (voting types disaggregated by candidate)

df_final_full_3 <- df_final_full_2 %>%
  inner_join(naes08_phone_full, by = c("ID" = "RKEY")) %>%
  group_by(Candidate, SINCERE_MAX2, STRATEGIC_MAX2, WEEK_c) %>%
  count() %>%
  mutate(sincere_strategic = case_when(
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 0) ~ 1,
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 0) ~ 2,
    (SINCERE_MAX2 == 0 & STRATEGIC_MAX2 == 1) ~ 3,
    (SINCERE_MAX2 == 1 & STRATEGIC_MAX2 == 1) ~ 4,
    )) %>%
  group_by(Candidate, WEEK_c) %>%
  mutate(percent = n / sum(n),
         df = "naes08_phone_d")

df_final_full_3 %>%
  filter(sincere_strategic == 2) %>%
  ggplot(aes(x = WEEK_c, y = percent, color = Candidate)) + 
    geom_point(size = 0.5) + 
    geom_smooth(method = "loess") +
    labs(
      title = "Expressive Voting Over Time",
      x = "Date",
      y = "Expressive Voters"
    )

df_final_full_3 %>%
  filter(sincere_strategic == 3) %>%
  ggplot(aes(x = WEEK_c, y = percent, color = Candidate)) + 
    geom_point(size = 0.5) + 
    geom_smooth(method = "loess") +
    labs(
      title = "Instrumental Voting Over Time",
      x = "Date",
      y = "Instrumental Voters"
    )

######################

# Viability -- Iowa Caucuses, respondents stratified by whether Iraq war was worth it
# No patterns found

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999)),
         CDb02_c %in% c(1, 2)) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  mutate(iraq_war = case_when(
    CDb02_c == 1 ~ "1 - Yes",
    CDb02_c == 2 ~ "2 - No"
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = NAa06_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa07_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa08_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    facet_wrap(~ iraq_war) +
    labs(
      title = "Attitudes Towards the Iraq War",
      subtitle = "2008 Democratic Nominating Contest (Iowa Caucuses)",
      x = "Month",
      y = "Viability Rating"
    )

# Viability -- Iowa Caucuses, respondents stratified by whether government should nationalize health care
# No patterns found

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999)),
         !(CCa01_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = NAa06_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa07_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa08_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    facet_wrap(~ CCa01_c) +
    labs(
      title = "Candidate Viability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest (Stratified by Views on Health Care)",
      x = "Month",
      y = "Viability Rating"
    )

# Viability -- Iowa Caucuses, respondents stratified by ideology
# No patterns found 

naes08_phone_full %>%
  filter(!(NAa06_c %in% c(998, 999)),
         !(NAa07_c %in% c(998, 999)),
         !(NAa08_c %in% c(998, 999)),
         !(MA04_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  mutate(iowa_caucuses = case_when(
    DATE_c <= "2008-01-03" ~ 0,
    DATE_c > "2008-01-03" ~ 1,
  )) %>%
  mutate(ideology = case_when(
    MA04_c == 1 ~ "1 - Very Conservative",
    # MA04_c == 2 ~ "2 - Moderate",
    # MA04_c == 3 ~ "2 - Moderate",
    # MA04_c == 4 ~ "2 - Moderate",
    MA04_c == 5 ~ "3 - Very Liberal"
  )) %>%
  ggplot(aes(x = DATE_c, group = iowa_caucuses)) +
    geom_smooth(aes(y = NAa06_c, color = "Clinton"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa07_c, color = "Edwards"), method = "loess", se = FALSE) +
    geom_smooth(aes(y = NAa08_c, color = "Obama"), method = "loess", se = FALSE) +
    scale_color_manual(name = "Candidate", values = colors) +
    geom_vline(xintercept = as.numeric(as.Date("2008-01-03")), linetype = 4) +
    facet_wrap(~ ideology, nrow = 3) +
    labs(
      title = "Candidate Viability (Iowa Caucuses)",
      subtitle = "2008 Democratic Nominating Contest (Stratified by Ideology)",
      x = "Month",
      y = "Viability Rating"
    )

##############

# Health care questions

naes08_phone_full %>%
  filter(!(CCa01_c %in% c(998, 999)),
         !(CCa04_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c)) + 
    geom_smooth(aes(y = CCa01_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = CCa04_c), method = "loess", se = FALSE) +
    labs(
      title = "Voters' Health Care Views Over Time"
    ) 

# Foreign policy questions

naes08_phone_full %>%
  filter(!(CDa02_c %in% c(998, 999)),
         !(CDb01_c %in% c(998, 999)),
         !(CDb02_c %in% c(998, 999)),
         !(CDb03_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c)) + 
    geom_smooth(aes(y = CDa02_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = CDb01_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = CDb02_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = CDb03_c), method = "loess", se = FALSE) +
    labs(
      title = "Voters' Foreign Policy Views Over Time"
    ) 

# Political orientation

naes08_phone_full %>%
  filter(!(MA04_c %in% c(998, 999)),
         !(MC01_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c)) + 
    geom_smooth(aes(y = MA04_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = MC01_c), method = "loess", se = FALSE) +
    labs(
      title = "Voters' Political Orientation Over Time"
    ) 

# Political media exposure (over time)
# No pattern

naes08_phone_full %>%
  filter(!(EB02_c %in% c(998, 999)),
         !(EC01_c %in% c(998, 999)),
         !(ED01_c %in% c(998, 999)),
         !(EE02_c %in% c(998, 999)),
         !(FC01_c %in% c(998, 999)),
         DATE_c <= "2008-06-08") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c)) + 
    geom_smooth(aes(y = EB02_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = EC01_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ED01_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = EE02_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = FC01_c), method = "loess", se = FALSE) +
    labs(
      title = "Voters' Political Media Exposure Over Time"
    ) 

# Political media exposure (Iowa caucuses)
# No pattern 

naes08_phone_full %>%
  filter(!(EB02_c %in% c(998, 999)),
         !(EC01_c %in% c(998, 999)),
         !(ED01_c %in% c(998, 999)),
         !(EE02_c %in% c(998, 999)),
         !(FC01_c %in% c(998, 999))) %>%
  filter(DATE_c <= "2008-01-08",
         DATE_c >= "2007-12-30") %>%
  group_by(DATE_c) %>%
  ggplot(aes(x = DATE_c)) + 
    geom_smooth(aes(y = EB02_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = EC01_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = ED01_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = EE02_c), method = "loess", se = FALSE) +
    geom_smooth(aes(y = FC01_c), method = "loess", se = FALSE) +
    labs(
      title = "Voters' Political Media Exposure Over Time"
    ) 
```
